MLVU information sheet

### 2024-03-29 paper/info_sheet.tex
added info sheet

\begin{tabular}{r r}
name &student number \\
\hline
Kai Niermann & 1234567 \\
Dávid Miklo & 1234567 \\
Trix Taiclet & 1234567 \\
Conner Dassen & 1234567 \\
Red Kaláb & 1234567 \\
\end{tabular}

@@

\paragraph{Use of AI tools} \textit{If you used tools like ChatGPT or Github Copilot in any phase of the report, please detail here which tools you used, what parts of the work you used them for and how. Note that if you use an AI tool and don't report it, it's considered fraud, so be detailed. Note also that having an AI tool write for you is not allowed. }

\paragraph{Link to code (optional)} \textit{If you would like to share your code, you can link to your repository here.}

\paragraph{Group disagreements} \textit{If there are any disagreements in the group, you may \textbf{not} remove a student from the author list without their consent. You should bring disagreements to our attention early. As a last resort, you can describe any grievances here}

>>>>

\begin{tabular}{r r}
name &student number \\
\hline
Kai Niermann & 2720905 \\
Dávid Miklo & 2767001 \\
Trix Taiclet & 2785891 \\
Conner Dassen & 2695049 \\
Red Kaláb & 2735630 \\
\end{tabular}

@@

\paragraph{Use of AI tools} \textit{}
\paragraph{Link to code (optional)} \textit{}

\paragraph{Group disagreements} \textit{}
